Uniform formula lower bounds for the satisfiability problem.

### 2022-06-28 article/main.tex
Update Title
Cleaning up

%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%
\title{Uniform formula lower bounds for testing the existence of and counting satisfiable assignments}
\author{Gabriel Bathie, Ryan Williams}
\begin{document}
\maketitle

\begin{abstract}
\end{abstract}

@@

A particular attention was dedicated to the \SAT{} problem, 
since a super-polynomial lower bound for this problem would imply $\NP \neq \P$
(for programs, $\NP \neq \textsf{P/poly}$ for circuits).

>>>>

%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%
\title{Uniform formula lower bounds for the satisfiability problem.}
\author{Gabriel Bathie, Ryan Williams}
\begin{document}
\maketitle

@@

A particular attention was dedicated to the \SAT{} problem, 
since a super-polynomial lower bound for this problem would imply $\NP \neq \Poly$
(for programs, $\NP \neq \textsf{P/poly}$ for circuits).
